Informing policy via dynamic models: Eliminating cholera in Haiti

### 2022-10-19 ms.Rnw
minor change, ready to compile from GL

# Create vectors for the unit and shared parameters
unit_specific_names <- c("betaB", "foi_add", "Binit")
shared_param_names <- c(
  "mu_B", "XthetaA", "thetaI", "lambdaR", "r", "std_W",
  "epsilon", "k", "sigma", "rho", "gamma"
)

@@

  SEARCH3 = list(
    TOP_N = 9,
    NBPF = 100,
    NP = 5000,
    SPAT_REGRESSION = 0.05,
    NREPS = 8,
    NP_EVAL = 5000,
    NREPS_EVAL = 18,
    RW_SD = chol_rw_3.sd,
    COOLING = 0.5,
    KEEP_TRACES = TRUE
  )

>>>>

# Create vectors for the unit and shared parameters
unit_specific_names <- c("betaB", "foi_add")
shared_param_names <- c(
  "mu_B", "XthetaA", "thetaI", "lambdaR", "r", "std_W",
  "epsilon", "k", "sigma", "rho", "gamma"
)

@@

  SEARCH3 = list(
    TOP_N = 9,
    NBPF = 100,
    NP = 5000,
    SPAT_REGRESSION = 0.05,
    NREPS = 8,
    NP_EVAL = 5000,
    NREPS_EVAL = 18,
    RW_SD = chol_rw_3.sd,
    COOLING = 0.5,
    KEEP_TRACES = TRUE,
    KEEP_LIK_MAT = TRUE
  )
